Creating optimal conditions for reproducible data analysis in \R with `fertile'\protect\thanks{The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the \pkg{tidyverse} team.}

### 2020-08-09 STAT-paper-template/APA/fertile.tex
added missing .tex file

\documentclass[APA,LATO1COL]{WileyNJD-v2}

@@

\raggedbottom

\begin{document}

@@

<<write_csv, include=FALSE>>=
readr::write_csv(mtcars, "~/Desktop/my_data.csv")
@

<<fertile, message = FALSE, error = TRUE>>=
library(fertile)
file.exists("~/Desktop/my_data.csv")
read.csv("~/Desktop/my_data.csv")
read.csv("../../../Desktop/my_data.csv")
@

@@

<<setwd, message=FALSE, error = TRUE>>=
setwd("~/Desktop")
@

@@

<<list-checks>>=
list_checks()
@

@@

<<set-project>>=
proj_dir <- "project_miceps"
@

<<echo=FALSE>>=
bad_file <- fs::path(proj_dir, "install_proj_packages.R")
if (file.exists(bad_file)) {
  fs::file_delete(bad_file)
}
@

<<proj_check_some, warning = FALSE>>=
proj_check_some(proj_dir, contains("paths"))
@

@@

<<proj_analyze, out.width = 180>>=
proj_analyze(proj_dir)
@

@@

<<read-csv, message=FALSE, include=FALSE>>=
library(purrr)
library(forcats)
read_csv(fs::path(proj_dir, "mice.csv"))
@

<<log-report>>=
log_report()
@

@@

<<log-clear, include=FALSE>>=
log_clear()
log_report()
@

@@

<<>>=
fertile::read_csv
@

@@

<<path checks, error = TRUE, message = FALSE>>=
# Path inside the directory
check_path("project_miceps")

# Absolute path (current working directory)
check_path(getwd())

# Path outside the directory
check_path("../fertile.Rmd")
@

@@

<<is_file>>=
is_data_file(fs::path(proj_dir, "mice.csv"))
is_image_file(fs::path(proj_dir, "proteins_v_time.png"))
is_text_file(fs::path(proj_dir, "README.md"))
is_r_file(fs::path(proj_dir, "analysis.Rmd"))
@

@@

<<sandbox>>=
proj_dir
fs::dir_ls(proj_dir) %>% head(1)
temp_dir <- sandbox(proj_dir)
temp_dir
fs::dir_ls(temp_dir) %>% head(1)
@

@@

<<proj_pkg_script, eval=TRUE, cache=TRUE>>=
install_script <- proj_pkg_script(proj_dir)
cat(readChar(install_script, 1e5))
@

>>>>

\documentclass[APA,LATO1COL]{WileyNJD-v2}\usepackage[]{graphicx}\usepackage[]{color}
% maxwidth is the original width if it is less than linewidth
% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

@@

\raggedbottom
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{library}\hlstd{(fertile)}
\hlkwd{file.exists}\hlstd{(}\hlstr{"~/Desktop/my_data.csv"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## [1] TRUE
\end{verbatim}
\begin{alltt}
\hlkwd{read.csv}\hlstd{(}\hlstr{"~/Desktop/my_data.csv"}\hlstd{)}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: Detected absolute paths}}\begin{alltt}
\hlkwd{read.csv}\hlstd{(}\hlstr{"../../../Desktop/my_data.csv"}\hlstd{)}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: Detected paths that lead outside the project directory}}\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{setwd}\hlstd{(}\hlstr{"~/Desktop"}\hlstd{)}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: setwd() is likely to break reproducibility. Use here::here() instead.}}\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{list_checks}\hlstd{()}
\end{alltt}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- The available checks in `fertile` are as follows: ---------------- fertile 0.0.0.9027 --}}\begin{verbatim}
##  [1] "has_tidy_media"          "has_tidy_images"        
##  [3] "has_tidy_code"           "has_tidy_raw_data"      
##  [5] "has_tidy_data"           "has_tidy_scripts"       
##  [7] "has_readme"              "has_no_lint"            
##  [9] "has_proj_root"           "has_no_nested_proj_root"
## [11] "has_only_used_files"     "has_clear_build_chain"  
## [13] "has_no_absolute_paths"   "has_only_portable_paths"
## [15] "has_no_randomness"
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{proj_dir} \hlkwb{<-} \hlstr{"project_miceps"}
\end{alltt}
\end{kframe}
\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{proj_check_some}\hlstd{(proj_dir,} \hlkwd{contains}\hlstd{(}\hlstr{"paths"}\hlstd{))}
\end{alltt}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Compiling... ----------------------------------------------------- fertile 0.0.0.9027 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Rendering R scripts... ------------------------------------------- fertile 0.0.0.9027 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Running reproducibility checks ----------------------------------- fertile 0.0.0.9027 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# v Checking for no absolute paths}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# v Checking for only portable paths}}\end{kframe}
\begin{kframe}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Summary of fertile checks ---------------------------------------- fertile 0.0.0.9027 --}}\end{kframe}
\begin{kframe}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# v Reproducibility checks passed: 2}}\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{proj_analyze}\hlstd{(proj_dir)}
\end{alltt}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Analysis of reproducibility for project\_miceps ------------------- fertile 0.0.0.9027 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Packages referenced in source code ----------------------------- fertile 0.0.0.9027 --}}\begin{verbatim}
## # A tibble: 9 x 3
##   package       N used_in                    
##   <chr>     <int> <chr>                      
## 1 broom         1 project_miceps/analysis.Rmd
## 2 dplyr         1 project_miceps/analysis.Rmd
## 3 ggplot2       1 project_miceps/analysis.Rmd
## 4 purrr         1 project_miceps/analysis.Rmd
## 5 readr         1 project_miceps/analysis.Rmd
## 6 rmarkdown     1 project_miceps/analysis.Rmd
## 7 skimr         1 project_miceps/analysis.Rmd
## 8 stargazer     1 project_miceps/analysis.Rmd
## 9 tidyr         1 project_miceps/analysis.Rmd
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Files present in directory ------------------------------------- fertile 0.0.0.9027 --}}\begin{verbatim}
##                      file   ext    size
## 1 Estrogen_Receptors.docx  docx  10.97K
## 2      citrate_v_time.png   png 188.08K
## 3     proteins_v_time.png   png 378.45K
## 4   Blot_data_updated.csv   csv  14.43K
## 5      CS_data_redone.csv   csv   7.39K
## 6                mice.csv   csv  14.33K
## 7               README.md    md      39
## 8            miceps.Rproj Rproj     204
## 9            analysis.Rmd   Rmd   4.94K
##                                                                      mime
## 1 application/vnd.openxmlformats-officedocument.wordprocessingml.document
## 2                                                               image/png
## 3                                                               image/png
## 4                                                                text/csv
## 5                                                                text/csv
## 6                                                                text/csv
## 7                                                           text/markdown
## 8                                                            text/rstudio
## 9                                                         text/x-markdown
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Suggestions for moving files ----------------------------------- fertile 0.0.0.9027 --}}\begin{verbatim}
##                  path_rel    dir_rel
## 1   Blot_data_updated.csv   data-raw
## 2      CS_data_redone.csv   data-raw
## 3 Estrogen_Receptors.docx inst/other
## 4            analysis.Rmd  vignettes
## 5      citrate_v_time.png inst/image
## 6                mice.csv   data-raw
## 7     proteins_v_time.png inst/image
##                                                                                                cmd
## 1     file_move('project_miceps/Blot_data_updated.csv', fs::dir_create('project_miceps/data-raw'))
## 2        file_move('project_miceps/CS_data_redone.csv', fs::dir_create('project_miceps/data-raw'))
## 3 file_move('project_miceps/Estrogen_Receptors.docx', fs::dir_create('project_miceps/inst/other'))
## 4             file_move('project_miceps/analysis.Rmd', fs::dir_create('project_miceps/vignettes'))
## 5      file_move('project_miceps/citrate_v_time.png', fs::dir_create('project_miceps/inst/image'))
## 6                  file_move('project_miceps/mice.csv', fs::dir_create('project_miceps/data-raw'))
## 7     file_move('project_miceps/proteins_v_time.png', fs::dir_create('project_miceps/inst/image'))
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Problematic paths logged --------------------------------------- fertile 0.0.0.9027 --}}\begin{verbatim}
## NULL
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{log_report}\hlstd{()}
\end{alltt}
\begin{verbatim}
## # A tibble: 3 x 4
##   path         path_abs                             func     timestamp          
##   <chr>        <chr>                                <chr>    <dttm>             
## 1 package:pur~ <NA>                                 base::l~ 2020-08-09 15:36:09
## 2 package:for~ <NA>                                 base::l~ 2020-08-09 15:36:09
## 3 project_mic~ /Users/audreybertin/Documents/ferti~ readr::~ 2020-08-09 15:36:09
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fertile}\hlopt{::}\hlstd{read_csv}
\end{alltt}
\begin{verbatim}
## function (file, ...) 
## {
##     if (interactive_log_on()) {
##         log_push(file, "readr::read_csv")
##         check_path_safe(file)
##         readr::read_csv(file, ...)
##     }
## }
## <bytecode: 0x7fc56efc82c8>
## <environment: namespace:fertile>
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{# Path inside the directory}
\hlkwd{check_path}\hlstd{(}\hlstr{"project_miceps"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## # A tibble: 0 x 3
## # ... with 3 variables: path <chr>, problem <chr>, solution <chr>
\end{verbatim}
\begin{alltt}
\hlcom{# Absolute path (current working directory)}
\hlkwd{check_path}\hlstd{(}\hlkwd{getwd}\hlstd{())}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: Detected absolute paths}}\begin{alltt}
\hlcom{# Path outside the directory}
\hlkwd{check_path}\hlstd{(}\hlstr{"../fertile.Rmd"}\hlstd{)}
\end{alltt}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: Detected paths that lead outside the project directory}}\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{is_data_file}\hlstd{(fs}\hlopt{::}\hlkwd{path}\hlstd{(proj_dir,} \hlstr{"mice.csv"}\hlstd{))}
\end{alltt}
\begin{verbatim}
## [1] TRUE
\end{verbatim}
\begin{alltt}
\hlkwd{is_image_file}\hlstd{(fs}\hlopt{::}\hlkwd{path}\hlstd{(proj_dir,} \hlstr{"proteins_v_time.png"}\hlstd{))}
\end{alltt}
\begin{verbatim}
## [1] TRUE
\end{verbatim}
\begin{alltt}
\hlkwd{is_text_file}\hlstd{(fs}\hlopt{::}\hlkwd{path}\hlstd{(proj_dir,} \hlstr{"README.md"}\hlstd{))}
\end{alltt}
\begin{verbatim}
## [1] TRUE
\end{verbatim}
\begin{alltt}
\hlkwd{is_r_file}\hlstd{(fs}\hlopt{::}\hlkwd{path}\hlstd{(proj_dir,} \hlstr{"analysis.Rmd"}\hlstd{))}
\end{alltt}
\begin{verbatim}
## [1] TRUE
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{proj_dir}
\end{alltt}
\begin{verbatim}
## [1] "project_miceps"
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(proj_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{1}\hlstd{)}
\end{alltt}
\begin{verbatim}
## project_miceps/Blot_data_updated.csv
\end{verbatim}
\begin{alltt}
\hlstd{temp_dir} \hlkwb{<-} \hlkwd{sandbox}\hlstd{(proj_dir)}
\hlstd{temp_dir}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/Rtmp0zg9IT/project_miceps
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(temp_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{1}\hlstd{)}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/Rtmp0zg9IT/project_miceps/Blot_data_updated.csv
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{install_script} \hlkwb{<-} \hlkwd{proj_pkg_script}\hlstd{(proj_dir)}
\hlkwd{cat}\hlstd{(}\hlkwd{readChar}\hlstd{(install_script,} \hlnum{1e5}\hlstd{))}
\end{alltt}
\begin{verbatim}
## # Run this script to install the required packages for this R project.
## # Packages hosted on CRAN...
## install.packages(c( 'broom', 'dplyr', 'ggplot2', 'purrr', 'readr', 'rmarkdown', 'skimr', 'stargazer', 'tidyr' ))
## # Packages hosted on GitHub...
\end{verbatim}
\end{kframe}
\end{knitrout}
